Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

\section{Additional Information}

\noindent\textbf{I. Potential Societal Impact.}

(1) \ul{Security:} Adversarial attacks may raise security considerations on
deep learning applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.

(2) \ul{Environment:} Although adversarial training is not
environment-friendly due to its high training cost (in terms of more intensive
computation than regular training), our method has significantly improved the
adversarial training efficiency compared to the previous works (hence is a
little bit more environment-friendly).

\noindent\textbf{II. Limitations.}

@@

(4) \ul{A factor that influence the performance of our approach, namely
backbone model.}

@@

(5) \ul{A factor that influence the performance of our approach, namely
adversarial training budget $\eta$.}

@@

\noindent\textbf{III. Use of Existing Assets.}

@@

\section{More Technical and Design Details}

@@

\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}

@@

\ul{Relationship with HM:}
%
Since EST only aims to maximize the embedding move distance off its original
location without specifying any direction, it leads to a random hardness
value.
%
Because the perturbed triplet can be either harder or easier than the benign
triplet.
%
Namely, EST merely indirectly increase the hardness of the training
triplet, and may even decrease its hardness.
%
Thus, EST suffers from inefficiency in adversarial training compared to HM.

\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}

@@

\ul{Relationship with HM:}

\oo{todo}

However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

>>>>

\tableofcontents

\section{Additional Information}
\label{sec:a}

\subsection{Potential Societal Impact.}

\noindent\textbf{I. Security.}

Adversarial attacks may raise security considerations on
deep learning applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.

~\newline
\noindent\textbf{II. Environment.}

Although adversarial training is not
environment-friendly due to its high training cost (in terms of more intensive
computation than regular training), our method has significantly improved the
adversarial training efficiency compared to the previous works (hence is a
little bit more environment-friendly).

\subsection{Limitations.}

\noindent\textbf{I. Assumptions.}

@@

~\newline
\noindent\textbf{II. Performance-Sensitive Factors.}

(1) \ul{Backbone deep neural network model.}

@@

Adversarial training requires more time and GPU memory than regular training.
%
The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
of memory per GPU in distributed data parallel mode, which is affordable to
most researchers in the community.
%
Adversarial training of ResNet-50 requires much more than 12GB of memory per
GPU, which will make it harder for some readers to reproduce the results
and compare.

(2) \ul{Adversarial training budget $\eta$.}

@@

(3) \ul{Source hardness $H_\mathsf{S}$ and destination hardness
$H_\mathsf{D}$.}

The source hardness $H_\mathsf{S}$ depends on triplet sampling strategy, which
is another research topic in the DML field.
%
The available triplet sampling strategies includes Random, Semihard, Softhard,
Distance-weighted, as well as within-batch Hardest sampling strategies.
%
We conduct experiments and figure out an appropriate choice in our experiments.

The range of choices for $H_\mathsf{D}$ is wider than that of $H_\mathsf{S}$.
%
When we use another benign sample triplet to calculate $H_\mathsf{D}$, the
``another benign sample triplet'' can be sampled with the existing triplet
sampling strategies as well.
%
We tested every combination of sampling strategies in our experiments.
%
Besides, $H_\mathsf{D}$ can be a pseudo-hardness function in order to avoid
disadvantages (discussed in our approach) of using another benign triplet as
reference.
%
Graduate Adversary is a family of such pseudo-hardness functions, and Linear
Graduate Adversary (LGA) is a simple and straightforward example which is
already effective.
%
Although $H_\mathsf{D}$ can be a constant as well, such choice lacks
flexibility and is only used for demonstrating the advantage of LGA in our
experiments.

~\newline
\noindent\textbf{III. Use of Existing Assets.}

@@

\section{More Technical and Design Details}
\label{sec:b}

@@

~\newline
\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}

@@

\ul{(1) Relationship with HM:}

Since EST only aims to maximize the embedding move distance off its original
location without specifying any direction, it leads to a random hardness value.
%
The expectation $E[H(\cdot)]$ of its resulting adversarial triplet is expected
to be close to $E[H_\mathsf{S}]$.
%
Because the perturbed triplet can be either harder or easier than the benign
triplet.
%
Namely, EST merely indirectly increase the hardness of the training triplet,
and may even decrease its hardness.
%
Thus, EST suffers from inefficiency in adversarial training compared to HM.

~\newline
\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}

@@

\ul{(1) Relationship with HM:}

When ACT successively ``collapses'' the positive and negative embedding
vectors together, the hardness will be zero, \ie, $E[H(\cdot)]=0$.
%
But ACT is not equivalent to $HM[\cdot,0]$ because the two methods have
different objectives and use different gradients.
%
Besides, in order to avoid the ``misleading gradients''~\cite{robrank}, ACT
fixes the anchor and only perturb the positive and negative samples, which
makes the objective for creating adversarial examples more difficult to
optimize in practice.
%
In brief, ACT is also indirectly increasing the loss value, suffering from
inefficient adversarial learning.

~\newline
\noindent\textbf{IV. Hardness Manipulation (HM).}
